Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
remv paranthesis

\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{Dyn}_{#1}(#2)}
%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #2 \; #1 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
%\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\langle#2\rangle\;#3\langle#4\rangle}
%\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
%\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\langle#2\rangle}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\langle#2\rangle}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D cast calculus on space-inefficient CEK
\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
\newcommand{\hiredruleS}[3]{\highlight{#1} & 
\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hypercoercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
% abbrev
\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
% names
\newcommand{\ineffCEK}{$\mathcal{C}$}
\newcommand{\ineffCEKD}{$\mathcal{D}$}
\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
\newcommand{\evalEqv}[2]{\ensuremath{eval_{\text{#1}} = eval_{\text{#2}}}}
\newcommand{\continue}[2]{cont(#2,#1)}
\newcommand{\highlight}[1]{{\color{red} #1}}

@@

	Reduction \fbox{$\judgeCreduce{s}{s}$}
	\[
	\begin{array}{rclr}
		\hiredrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{
			\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa}
%			\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa
		}
	}{}
	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{(\kOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{(\kOOinl{\kappa})}
	}{}
	\redrule{
	\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{(\kOOinr{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{(\kOOappI{e_2}{\rho}{\kappa})}}{}

\redrule{
\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
\sOOinspect{e}{\rho}{(\kOOcar{\kappa})}}{}

\redrule{
	\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
	\sOOinspect{e}{\rho}{(\kOOcdr{\kappa})}}{}

\redrule{
\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
\sOOinspect{e_1}{\rho}{(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}

\redrule{
\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOconsII{v_1}{\kappa})}}{}

\redrule{
\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
\sOOreturn{(\vOOcons{v_1}{v_2})}{\kappa}}{}

\redrule{
\sOOreturn{v}{(\kOOinl{\kappa})}}{
\sOOreturn{(\vOOinl{v})}{\kappa}}{}

\redrule{
\sOOreturn{v}{(\kOOinr{\kappa})}}{
\sOOreturn{(\vOOinr{v})}{\kappa}}{}

\redrule{
\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}

\redrule{
\sOOreturn{v_2}{(\kOOappII{(\vOOfun{\rho}{x}{e})}{\kappa})}}{
\sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
	\hiredrule{
		\sOOreturn{v_1}{
			\kOOappII{\vOOcast{v_2}{
					\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			}}{\kappa}
%			(\mathtt{app_2} \; \vOOcast{v_2}{
%				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
%			} \; \kappa)
		}
	}{
		\sOOreturn{v_1}{
			\kOOcast{\cOOcast{T_3}{l}{T_1}}{
				\kOOappII{v_2}{
					\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa}
				}
			}
%			\langle\rangle
%			(\mathtt{app_2} \; v_2 \; 
%			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
		}
	}{}
	\redrule{
	\sOOreturn{
		(\vOOcons{v_1}{v_2})
	}{(\kOOcar{\kappa})}
	}{
	\sOOreturn{v_1}{\kappa}
	}{}
	\hiredrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{(\mathtt{fst} \; \kappa)}
	}{
		\sOOreturn{v}{
			\kOOcar{
				\kOOcast{\cOOcast{T_1}{l}{T_3}}{\kappa}
			}}
	}{}
	\redrule{
	\sOOreturn{
		(\vOOcons{v_1}{v_2})
	}{(\kOOcdr{\kappa})}
	}{
	\sOOreturn{v_2}{\kappa}
	}{}

	\hiredrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{(\mathtt{snd} \; \kappa)}
	}{
		\sOOreturn{v}{
			\kOOcdr{\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa}}}
	}{}

\redrule{
\sOOreturn{v_1}{(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})}}{}

\redrule{
\sOOreturn{v_2}{(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})}}{
\sOOinspect{e_3}{\rho}{
	(\kOOcaseIII{v_1}{v_2}{\kappa})
}}{}

\redrule{
\sOOreturn{v_3}{
	(\kOOcaseIII{(\vOOinl{v})}{v_2}{\kappa})
%	(\mathtt{case_3}\;(\vOOinl{v})\;v_2\;\kappa)
}
}{
\sOOreturn{v}{(\kOOappII{v_2}{\kappa})}
}{}

\redrule{
	\sOOreturn{v_3}{
		(\kOOcaseIII{(\vOOinr{v})}{v_2}{\kappa})
%		(\mathtt{case_3}\;(\vOOinr{v})\;v_2\;\kappa)
	}
}{
\sOOreturn{v}{(\kOOappII{v_3}{\kappa})}
}{}

\redrule{
	\highlight{\sOOreturn{v_3}{
		(	\kOOcaseIII{
				\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
			}{v_2}{\kappa})
%		
%			(\mathtt{case_3}\;
%		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
%		\;v_2\;\kappa)
	}}
}{
	\highlight{\sOOreturn{v_3'}{
			(\kOOcaseIII{v}{v_2'}{\kappa})
	}}
}{\\&&
\highlight{\text{where}\;
v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}}
\\&&
\highlight{\text{and}\;
v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}}
}

	\redrule{
		\highlight{\sOOreturn{v}{(
				\kOOcast{c}{\kappa}
			)}}
	}{
\highlight{          
\begin{cases}
	\sOOreturn{v'}{\kappa} & \sidecond{applyCast(v,c) = \rOOsucc{v'}}
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
\end{cases}}
	}{}
\redrule{
\sOOreturn{v}{\kOOmt}}{
\sOOhalt{observe(v)}}{}
	\end{array}
	\]

	Evaluation \fbox{$\judgeCeval{e}{o}$}
	\[
	\inference{
		\sOOinspect{e}{\emptyset}{wrap(\hckOOmt)} \longrightarrow_{B}^{*} 
		\sOOhalt{o}
	}{
		\judgeCeval{e}{o}
	}
	\]

@@

Before turning to the definition of the abstract data types, we first
give the definition of values and cast results used by the \effCEK{C}, as they 
are mentioned in the definition of the ADTs. The notation \hcvOOinj{P}{v} 
stands for values that are cast to the dynamic type.

\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
   and should be explained. -JS
\\---\\
I switch to the standard notation because we have an observation $\oOOinj$ -KC}

>>>>

\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{Dyn}_{#1}(#2)}
%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #2 \; #1 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
%\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\langle#2\rangle\;#3\langle#4\rangle}
%\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
%\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\langle#2\rangle}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\langle#2\rangle}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D cast calculus on space-inefficient CEK
\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{x}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{x}}^{*} #2}
\newcommand{\judgeCeval}[2]{eval_{\mathcal{x}}(#1) = #2}
\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{x} & #2 & #3\\}
\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{x}} 
& \highlight{#2} & \highlight{#3} \\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
\newcommand{\hiredruleS}[3]{\highlight{#1} & 
\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hypercoercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
% abbrev
\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
% names
\newcommand{\ineffCEK}{$\mathcal{C}$}
\newcommand{\ineffCEKD}{$\mathcal{D}$}
\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
\newcommand{\evalEqv}[2]{\ensuremath{eval_{\text{#1}} = eval_{\text{#2}}}}
\newcommand{\continue}[2]{cont(#2,#1)}
\newcommand{\highlight}[1]{{\color{red} #1}}

@@

	Reduction \fbox{$\judgeCreduce{s}{s}$}
	\[
	\begin{array}{rclr}
		\hiredrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{
			\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa}
%			\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa
		}
	}{}
	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{\kOOconsI{e_2}{\rho}{\kappa}}
	}{}
	\redrule{
		\sOOinspect{\eOOinl{e}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\kOOinl{\kappa}}
	}{}
	\redrule{
	\sOOinspect{\eOOinr{e}}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{\kOOinr{\kappa}}
	}{}
	\redrule{
		\sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{\kOOappI{e_2}{\rho}{\kappa}}}{}

\redrule{
\sOOinspect{\eOOcar{e}}{\rho}{\kappa}}{
\sOOinspect{e}{\rho}{\kOOcar{\kappa}}}{}

\redrule{
	\sOOinspect{\eOOcdr{e}}{\rho}{\kappa}}{
	\sOOinspect{e}{\rho}{\kOOcdr{\kappa}}}{}

\redrule{
\sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\rho}{\kappa}}{
\sOOinspect{e_1}{\rho}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}}{}

\redrule{
\sOOreturn{v_1}{\kOOconsI{e_2}{\rho}{\kappa}}}{
\sOOinspect{e_2}{\rho}{\kOOconsII{v_1}{\kappa}}}{}

\redrule{
\sOOreturn{v_2}{\kOOconsII{v_1}{\kappa}}}{
\sOOreturn{\vOOcons{v_1}{v_2}}{\kappa}}{}

\redrule{
\sOOreturn{v}{\kOOinl{\kappa}}}{
\sOOreturn{\vOOinl{v}}{\kappa}}{}

\redrule{
\sOOreturn{v}{\kOOinr{\kappa}}}{
\sOOreturn{\vOOinr{v}}{\kappa}}{}

\redrule{
\sOOreturn{v_1}{\kOOappI{e_2}{\rho}{\kappa}}}{
\sOOinspect{e_2}{\rho}{\kOOappII{v_1}{\kappa}}}{}

\redrule{
\sOOreturn{v_2}{\kOOappII{\vOOfun{\rho}{x}{e}}{\kappa}}}{
\sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
	\hiredrule{
		\sOOreturn{v_1}{
			\kOOappII{\vOOcast{v_2}{
					\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			}}{\kappa}
%			(\mathtt{app_2} \; \vOOcast{v_2}{
%				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
%			} \; \kappa)
		}
	}{
		\sOOreturn{v_1}{
			\kOOcast{\cOOcast{T_3}{l}{T_1}}{
				\kOOappII{v_2}{
					\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa}
				}
			}
%			\langle\rangle
%			(\mathtt{app_2} \; v_2 \; 
%			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa}
		}
	}{}
	\redrule{
	\sOOreturn{
		\vOOcons{v_1}{v_2}
	}{\kOOcar{\kappa}}
	}{
	\sOOreturn{v_1}{\kappa}
	}{}
	\hiredrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{\mathtt{fst} \; \kappa}
	}{
		\sOOreturn{v}{
			\kOOcar{
				\kOOcast{\cOOcast{T_1}{l}{T_3}}{\kappa}
			}}
	}{}
	\redrule{
	\sOOreturn{
	\vOOcons{v_1}{v_2}
	}{\kOOcdr{\kappa}}
	}{
	\sOOreturn{v_2}{\kappa}
	}{}

	\hiredrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{\mathtt{snd} \; \kappa}
	}{
		\sOOreturn{v}{
			\kOOcdr{\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa}}}
	}{}

\redrule{
\sOOreturn{v_1}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}}{
\sOOinspect{e_2}{\rho}{\kOOcaseII{v_1}{e_3}{\rho}{\kappa}}}{}

\redrule{
\sOOreturn{v_2}{\kOOcaseII{v_1}{e_3}{\rho}{\kappa}}}{
\sOOinspect{e_3}{\rho}{
	\kOOcaseIII{v_1}{v_2}{\kappa}
}}{}

\redrule{
\sOOreturn{v_3}{
	\kOOcaseIII{\vOOinl{v}}{v_2}{\kappa}
}
}{
\sOOreturn{v}{\kOOappII{v_2}{\kappa}}
}{}

\redrule{
	\sOOreturn{v_3}{
		\kOOcaseIII{\vOOinr{v}}{v_2}{\kappa}
	}
}{
\sOOreturn{v}{\kOOappII{v_3}{\kappa}}
}{}

\redrule{
	\highlight{\sOOreturn{v_3}{
		\kOOcaseIII{
				\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
			}{v_2}{\kappa}
	}}
}{
	\highlight{\sOOreturn{v_3'}{
			\kOOcaseIII{v}{v_2'}{\kappa}
	}}
}{\\&&
\highlight{\text{where}\;
v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}}
\\&&
\highlight{\text{and}\;
v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}}
}

	\redrule{
		\highlight{\sOOreturn{v}{
				\kOOcast{c}{\kappa}
			}}
	}{
\highlight{          
\begin{cases}
	\sOOreturn{v'}{\kappa} & \sidecond{applyCast(v,c) = \rOOsucc{v'}}
	\\
	\sOOhalt{\oOOblame{l}} & \sidecond{applyCast(v,c) = \rOOfail{l}}
\end{cases}}
	}{}
\redrule{
\sOOreturn{v}{\kOOmt}}{
\sOOhalt{observe(v}}{}
	\end{array}
	\]

	Evaluation \fbox{$\judgeCeval{e}{o}$}
	\[
	\inference{
		\judgeCreduceTrans{
			\sOOinspect{e}{\emptyset}{\hckOOmt}
		}{\sOOhalt{o}}		
	}{
		\judgeCeval{e}{o}
	}
	\]

@@

Before turning to the definition of the abstract data types, we first
give the definition of values and cast results used by the \effCEK{C}, as they 
are mentioned in the definition of the ADTs. The notation $\hcvOOinj{P}{v}$ 
stands for values that are cast to the dynamic type, as in ...

\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
   and should be explained. -JS
\\---\\
I switch to the standard notation because we have an observation $\oOOinj$
But I forget the origin of this notation, can Jeremy cite it?
 -KC}
